Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-19 paper/paper.results.tex
Remove "Plot of.." in figure captions

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_requests}
	\caption{Plot of average runtime for LP with an increasing number of requests per clinician}
	\label{fig:avg-runtime-requests}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_blocks}
	\caption{Plot of average runtime for LP with an increasing number of 2-week blocks}
	\label{fig:avg-runtime-blocks}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_requests}
	\caption{Average runtime for LP with an increasing number of requests per clinician}
	\label{fig:avg-runtime-requests}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_blocks}
	\caption{Average runtime for LP with an increasing number of 2-week blocks}
	\label{fig:avg-runtime-blocks}
\end{figure}
